Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-02-26 Paper/RSVOptimization.rnw
Mucking around with knitr integration
Typo

\documentclass[10pt,letter,twoside]{article}

@@

\usepackage{multicol,float}
\floatplacement{figure}{H}
\raggedcolumns

\input{structure.tex}
\edef\figuresDir{\Sexpr{figuresDir}}

\title{Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
\def\headertitle{Assessment and optimization of RSV prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}

@@

\pagestyle{empty}
\begin{document}

@@

We then compared those regimens to the one recommended by AAP and to the six spatially adjusted alternatives (with no calendrical rounding) discussed above.

>>>>

\documentclass[10pt,letter]{article}
\usepackage{multicol,float}
\floatplacement{figure}{H}
\raggedcolumns

\input{structure.tex}

@@

\edef\figuresDir{\Sexpr{figuresDir}}
\title{Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
\def\headertitle{Assessment and optimization of RSV prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}

@@

\pagestyle{empty}
\begin{document}
% \SweaveOpts{concordance=TRUE}

@@

We then compared those regimens to the one recommended by the AAP and to the six spatially adjusted alternatives (with no calendrical rounding) discussed above.
